---
title: "Calculus I Last Grade Report for `r student`"
#title: "Calculus I Last Grade Report for John Doe"
author: "Jason E. Miller, Ph.D."
graphics: yes
output: 
  tufte::tufte_handout:
    keep_tex: true
    keep_md: true
header-includes:
   - \usepackage{rotating, booktabs,xcolor}
date: "`r Sys.Date()`"


# from https://www.reed.edu/data-at-reed/software/R/markdown_multiple_reports.html
# render with console command:  rmarkdown::render("report_script.Rmd")
---

```{r, echo=FALSE}
suppressWarnings(suppressPackageStartupMessages(library(dplyr)))
suppressWarnings(suppressPackageStartupMessages(library(leaflet)))
suppressWarnings(suppressPackageStartupMessages(library(DT)))
suppressWarnings(suppressPackageStartupMessages(library(stringr)))
library(knitr)
library(markdown)
library(rmarkdown)
```

```{r, echo=FALSE}
#student<-"Pydde"
# 'student' is passed from an R script
# here we find the index (which we name 'stuno', student number) in the mastery table that corresponds to this student
stuno<-grep(student, colnames(mastery))

# WANT:  dictionary that takes student ID and maps it to student's first and last names for customization purposes, below
```

The main table in this report lists the learning targets that are available for assessment at this point in the semester.  Your goal is to provide evidence of your mastery of as many learning targets as possible by the end of the semester.  

Those learning targets that you have not assessed yet are clearly indicated by a 'Not attempted'.  Next to those you have attempted is a symbol that indicates your level of mastery of that learning target.  These symbols mean

\begin{tabular}{ccl}
S & -- & Your work has provided satisfactory evidence of mastery \\
&& of the learning target.  \\
I & -- & Your work has provided insufficient evidence of mastery \\
&& of the learning target.  You should study the topic some \\
&&more and reassess.  \\
N & -- & Your work has provided no evidence of mastery of the \\
&&learning target.  You may not reassess the topic.  \\
\end{tabular}

\medskip

\noindent To date, this is my record of our learning targets and your assessments: 
```{r table, echo=FALSE,R.options=knitr::opts_chunk$set(warning=FALSE, message=FALSE)}

# want a two-column table
ttlrows<-dim(mastery[,c(1,stuno)])[1]
halfrows<-round(dim(mastery[,c(1,3)])[1]/2)
restrows<-ttlrows-halfrows

# need to select the column according to the 'student' passed to this script
t1<-kable(mastery[1:halfrows,c(1,stuno)],row.names=FALSE, format = "latex", booktabs = TRUE)
t2<-kable(mastery[(halfrows+1):ttlrows,c(1,stuno)],row.names=FALSE, format = "latex", booktabs = TRUE)

MU<-length(dcumprogressU[,stuno])
MS<-length(dcumprogressS[,stuno])
attempts<-sum(counts[,stuno])
progress<-counts[1,stuno]

grade<-
  if (progress>=21) {
    "A"} else { 
      if (progress>=15& progress<21) {
        "B"} else { 
      if (progress>=10 & progress<15) {
        "C"} else { 
      if (progress>=6 & progress<10) {
        "D"} else {
      "F"}
        }
      }
    }

message<-if (grade=="F") {"\\textbf{This is insufficient for passing the course.}"} else {
  paste("\\textbf{This meets the requirement of earning a", grade, "in the course.}",sep=" ")
}

```

\begin{table}[!htb]
\begin{minipage}{.5\linewidth}
      \centering
        {`r t1`}
    \end{minipage}%
    \begin{minipage}{.5\linewidth}
      \centering
        {`r t2`}
        \end{minipage} 
\end{table}

You have taken `r attempts+progress` learning target quizzes and shown sufficient evidence of mastery on `r progress` different learning targets. `r message`

```{r progressplot, echo=FALSE, include=FALSE}

tmp_progress<-progress.plot(student)
#tmp<-plot(1:3,3:1)
tmp_attempts<-attempts.plot(student)
```

\begin{center}
\includegraphics[width=6in]{`r tmp_progress`}

\includegraphics[width=6in]{`r tmp_attempts`}
\end{center}

\noindent If you received this report in error, please delete it and notify Dr. Miller by email\footnote{\texttt{jason.miller@csuci.edu}} of the error.




